\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{enumitem}

% Sobrescribir estilos para nombre
\renewcommand*{\namefont}{\color{black}\bfseries\Huge}
\renewcommand*{\namestyle}[2]{\namefont #1~#2}

% Sobrescribir estilos para secciones
\renewcommand{\sectionfont}{\color{black}\Large\bfseries}
\renewcommand{\subsectionfont}{\color{black}\large\bfseries}

\name{\textbf{\textcolor{black}{Ronald}}}{\textbf{\textcolor{black}{Mego}}}

\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\ %
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}

\begin{document}

\makecvtitle
\vspace*{-12mm}

\begin{center}\textbf{Chief Data Analytics Officer (CDAO) | MBA \& B.Sc. in Statistics | Machine Learning | Artificial Intelligence}\end{center}

\vspace{-1.7em}

\begin{center}
\begin{tabular}{ c c c c c c }
\faMobile {+507 64654515} & \enspace  \emailsymbol {ronald.mego@outlook.com} & \enspace \faHome {Panama City, PA} & 
\enspace \faGlobe \href{{https://ronaldmego.github.io/}}{\textcolor{blue}{Web}} &
\enspace \faGithub \href{{https://github.com/ronaldmego}}{\textcolor{blue}{github}} &
\enspace \faLinkedin \href{{https://www.linkedin.com/in/ronaldmego/}}{\textcolor{blue}{LinkedIn}}
\end{tabular}
\end{center}

\vspace{-1.5em}

\section{Profile}
{Ronald is a senior Data professional with over 15 years of experience leading data-driven strategies across Telecommunications, Fintech, and Digital industries. He has a hybrid profile in Analytics, Technology, and Business, which has enabled him to lead projects in Data Governance, Data Science, Machine Learning, Artificial Intelligence, and Data Monetization, focusing on driving value through data efficiently, optimizing budgets, and achieving monetizable results in finance, growth, and customer experience. He has led multicultural data-teams across countries and coordinated with global vendors. In projects, Ronald translates complex statistical concepts using Data Storytelling and visualization tools, presenting actionable insights to senior stakeholders in a clear and compelling way. He is proficient in programming languages like SQL, Python, and R, and combines a strong background in Statistics with an MBA. This allows him to transform mathematical, statistical, and computer science foundations into strategic value for the business while fostering a strong Data Culture in the team and the organization. Ronald has held roles such as Data Team Manager, Sr. Data Analyst, Sr. Data Scientist, and Sr. Data Engineer.}

\vspace{-0.5em}

\section{Professional Experience}

\customcventry{08/2023 ‐ present}{\color{blue}\href{https://www.millicom.com/}{Millicom | Tigo}}{Regional Head of Data (CDAO)}{Panama City, PA}{}{{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}, itemsep=-0.2em]
\item Design and lead advanced analytics frameworks and standards across countries, ensuring data quality and consistency, driving advanced customer segmentation, predictive analytics, and 1st-party data monetization, generating new revenue streams.
\item Spearhead Millicom’s Artificial Intelligence roadmap across countries, implementing innovative AI solutions such as RAG-based LLM Chatbots for analytics-driven automation and insights generation, enabling data-informed decisions, improving customer service processes, and driving operational efficiencies.
\item Build and execute the Regional Data Roadmap, achieving a 35\% YoY cost optimization by migrating over 400 processes and 70 dashboards from Tableau to Power BI and transitioning Snowflake and AWS workloads, while maintaining seamless delivery of insights and analytical capabilities across the organization.
\item Establish and monitor Data Governance practices for 50MM Telco and 5MM MFS users, ensuring data quality and providing accurate data and reports to HQ, specialized teams, and global stakeholders.
\item Lead a team of 9 direct reports and oversee indirect teams across countries, coordinating with global vendors and senior leadership to align analytics initiatives with organizational priorities and deliver impactful results.
\end{itemize}
\vspace{-0.1em}
}}

\customcventry{12/2021 ‐ 07/2023}{\color{blue}\href{https://www.millicom.com/}{Millicom | Tigo}}{Regional Head of Customer Intelligence}{Panama City, PA}{}{{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}, itemsep=-0.2em]
\item Design and lead the Customer Intelligence strategy across 6 countries, driving customer engagement, loyalty, and revenue growth by integrating advanced analytics with business objectives, reporting directly to the CMO.
\item Develop and implement customer behavior models, including lifetime value (LTV) and marketing mix analytics, optimizing marketing budgets, reducing churn by 10 p.p., and driving measurable revenue growth.
\item Introduce revenue analytics through RGUs segmentation, designing next best offer (NBO) strategies with dynamic data pipelines, achieving up to 5\% elasticity in targeted campaigns and enhancing personalization.
\item Build and deploy customer behavioral segmentation models to personalize loyalty and engagement campaigns using tools like Braze and AWS, reducing customer acquisition costs (CAC) and increasing conversion rates by 5 p.p.
\item Establish and grow the analytics team from the ground up, accelerating insights delivery, standardizing reporting processes, and fostering a data-driven culture across headquarters and regional operations.
\item Lead a team of 8 direct reports and oversee indirect teams across the region, ensuring alignment with strategic goals and delivering actionable insights to senior stakeholders.
\end{itemize}
\vspace{-0.1em}
}}

\customcventry{11/2019 ‐ 11/2021}{\color{blue}\href{https://grupoelcomercio.com.pe/}{Grupo El Comercio}}{Data Manager}{Lima, PE}{}{{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}, itemsep=-0.2em]
\item Develop user segmentation models and content recommendation models, supporting business objectives related to subscription growth and engagement.
\item Manage analytics tools to grow digital audiences, using real-time A/B testing with Chartbeat and Comscore.
\item Lead data architecture projects using BigQuery and QlikView for the administration of the digital group’s data.
\item Implement a zero and 1st (first) party data consolidation project into a golden record, enabling audience data monetization and the generation of new revenue streams.
\item Develop B2B and B2C dashboards to support strategies for digitalization and data monetization in programmatic advertising, using Google Analytics and Chartbeat.
\item Lead and promote the adoption of automation through RPA (Robotic Process Automation) with Artificial Intelligence, successfully automating manual tasks between accounting operations and the reading of KPIs from various external sources.
\item Supervise and guide a team of 8 direct reports, ensuring alignment with business goals.
\end{itemize}
\vspace{-0.1em}
}}

\customcventry{11/2016 ‐ 10/2019}{\color{blue}\href{https://telefonica.com.pe/}{Telefonica | Movistar}}{Customer Insights Manager}{Lima, PE}{}{{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}, itemsep=-0.2em]
\item Manage and model data for 17 million customers across home, prepaid, and postpaid products, establishing a single source of truth (SSOT) to support the Customer 360 business strategy, enhancing customer satisfaction and campaign effectiveness.
\item Develop dashboards for sales, collections, and customer support, and implement the first text mining model to analyze customer satisfaction in chatbot interactions.
\item Provide advanced fraud detection analytics to identify sales fraud among channels, partners, and vendors.
\item Supervise and guide a team of 15 direct reports, ensuring alignment with business goals.
\end{itemize}
\vspace{-0.1em}
}}

\customcventry{08/2009 ‐ 10/2016}{\color{blue}\href{https://telefonica.com.pe/}{Telefónica | Movistar}}{Customer Data Specialist}{Lima, PE}{}{{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}, itemsep=-0.2em]
\item Delivered robust, customer-centric, and commercially monetizable data solutions, earning outstanding recognition for achievements.
\item Developed analytical models for marketing, sales, customer experience, and collections, optimizing strategies for B2C mobile prepaid, postpaid, and home services.
\end{itemize}
\vspace{-0.1em}
}}

\customcventry{03/2016 ‐ 08/2016}{\color{blue}\href{https://portal.uni.edu.pe/}{Universidad Nacional de Ingenieria}}{Professor of Applied Computational Statistics}{Lima, PE}{}{{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}, itemsep=-0.2em]
\item Utilize innovative teaching methods and interactive tools to simplify complex statistical concepts, resulting in a 20\% reduction in student dropout rates and increased confidence in learning.
\item Design and execute curriculum incorporating real-world business case studies and data analysis projects, effectively bridging the gap between theoretical knowledge and practical application.
\item Mentor students on academic and career paths in data science and statistics, with several students successfully securing internships and roles in top-tier companies.
\end{itemize}
\vspace{-0.1em}
}}


\vspace{-0.8em}

\section{Education}

\customcventry{2005-2011}{\color{blue}\href{https://www.credential.net/922f2fe3-2fe4-4233-bbb6-1579ff468aa9?username=ronaldfriizmegosolano20070}{Universidad Nacional de Ingenieria}}{BSc. Applied Statistics}{Lima, Peru}{}{Thesis Project: “Segmentation of subscribers by traffic consumption in prepaid lines of Telefonica using k-means multivariate cluster analysis”. Top student, outstanding grade.}

\customcventry{2016-2018}{\color{blue}\href{https://www.credential.net/f953e37b-11e7-4570-89aa-6f21d606132d?username=ronaldfriizmegosolano20070}{PAD Business School}}{Master in Business Administration (MBA)}{Lima, Peru}{}{Thesis Project: “Application of non-operational troubleshooting of Telefonica and its sales channels”. Outstanding grade.}

\customcventry{2024-2024}{\color{blue}\href{https://www.credential.net/f6bd85db-4850-4f50-9609-7990eb0aaadc}{Massachusetts Institute of Technology}}{Diploma Data Leadership & Leveraging Data Systems}{Cambridge, MA, USA}{}{Participated in an immersive program with leaders in data management at the MIT Executive Program.}


\vspace{-0.8em}


\section{Specialized Programs and Diplomas}
{\begin{itemize}[label=\textbullet, itemsep=-0.2em]
\item Data Monetization, Management, and Trends (May. 2024) - \underline{\color{blue}\href{https://courses.edx.org/certificates/447c3529a7dc42aa8bf27297a97b0c88}{IEUniversity \& edX}}
\item Data Strategy: Data as Competitive Advantage (Jan. 2022) - \underline{\color{blue}\href{https://certificates.emeritus.org/39607ed0-10b6-4387-be32-5b34af6a5040}{Berkeley Executive Education}}
\item Entrepreneurship and Innovation Program (May. 2018) - \underline{\color{blue}\href{https://www.credential.net/54b357e1-243e-47ea-a40f-bcfdcfa04b18?username=ronaldfriizmegosolano20070}{Darden School of Business - Charlottesville, VA, USA}}
\item Diploma in Applied Finance (Jul. 2012) - \underline{\color{blue}\href{https://www.credential.net/322f33cb-ee81-453d-994a-3f81db550be9?username=ronaldfriizmegosolano20070}{Universidad del Pacifico}}
\end{itemize}}

\section{Technical Skills and Certifications}
{\begin{itemize}[label=\textbullet, itemsep=-0.2em]
\item AWS Cloud Certified Cloud Practitioner (Apr. 2024) - \underline{\color{blue}\href{https://www.credly.com/badges/b1438ac5-468e-4964-b6ac-2894b7e2204b/linked_in_profile}{Amazon Web Services}}
\item Cloud Data en Azure (Dec. 2023) - \underline{\color{blue}\href{https://www.credential.net/f49190f2-99e2-4af9-83a9-26bef312b87f?username=ronaldfriizmegosolano20070}{Bootcamp Institute \& Microsoft}}
\item GCP, Big Data and ML (May. 2020) - \underline{\color{blue}\href{https://www.coursera.org/account/accomplishments/certificate/RPWJ8S2L8CYW}{Coursera \& Google}}
\item Data Science in Python (Aug. 2020) - \underline{\color{blue}\href{https://www.coursera.org/account/accomplishments/verify/MYX5XU65HP95}{Coursera \& University of Michigan}}
\end{itemize}}


\vspace{-1.5em}

\section{Skills}
\begin{itemize}[label=\textbullet, itemsep=-0.2em]
\item \textbf{Data Story Telling}: PowerBI, Shiny, Streamlit, Tableau, Looker Studio, QuickSight
\item \textbf{Programming and Cloud}: R, Python, SQL, Spark, Snowflake, Redshift, BigQuery, Synapse, CI/CD, ML Ops, Airflow
\item \textbf{Machine Learning and AI}: Statistical Modeling, PyTorch, TensorFlow, SageMaker, OpenAI, LangChain, RAG, Bedrock
\item \textbf{Soft Skills}: Leadership, Communication, Team Collaboration, Problem Solving, Presentation Skills
\end{itemize}


\vspace{-1.5em}

\section{Languages}
\begin{multicols}{2}
\begin{itemize}[label=\textbullet, itemsep=-0.2em]
\item \textbf{English} [Fluent]
\item \textbf{Spanish} [Fluent] - Native
\end{itemize}
\end{multicols}


\end{document}